A pipeline to analyse time-course gene expression data

### 2019-10-08 manuscript.tex
Deploy NelleV/2019timecourse-rnaseq-pipeline to github.com/NelleV/2019timecourse-rnaseq-pipeline.git:gh-pages

\textbf{EAP}: this makes it sound like you create a class, but in fact it's just a list. Wouldn't it be helpful to make it a class?

@@

\CommentTok{# The function takes the data (data.frame or named matrix), the meta data}
\CommentTok{# (data.frame containing a timepoint and group column, the first corresponding}
\CommentTok{#<c2><a0>to the time-course information, the latter corresponding to the}
\CommentTok{# treatment).}
\NormalTok{pvalues =}\StringTok{ }\KeywordTok{DE_timecourse}\NormalTok{(}
\NormalTok{    data, moanin_model, timecourse_contrasts,}
    \DataTypeTok{use_voom_weights=}\OtherTok{FALSE}\NormalTok{)}
\NormalTok{qvalues =}\StringTok{ }\KeywordTok{apply}\NormalTok{(pvalues, }\DecValTok{2}\NormalTok{, p.adjust)}
\end{Highlighting}
\end{Shaded}

\textbf{EAP: is there a reason that the qvalues aren't provided with the output like in \texttt{DE\_timepoints}? Doesn't that risk the user not taking that step and working with the unadjusted p-values?}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{pvalue =}\StringTok{ }\NormalTok{qvalues[, }\StringTok{"M-K"}\NormalTok{]}
\NormalTok{lfc_timecourse =}\StringTok{ }\NormalTok{log_fold_change_timecourse[, }\StringTok{"M-K"}\NormalTok{]}
\KeywordTok{names}\NormalTok{(lfc_timecourse) =}\StringTok{ }\KeywordTok{row.names}\NormalTok{(log_fold_change_timecourse)}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Then rank by fisher's p-value and take max the number of genes of interest}
\CommentTok{# Filter out q-values for the pvalues table}
\NormalTok{fishers_pval =}\StringTok{ }\KeywordTok{pvalues_fisher_method}\NormalTok{(pvalues)}
\NormalTok{fishers_qval =}\StringTok{ }\KeywordTok{p.adjust}\NormalTok{(fishers_pval)}

@@

\textbf{EAP: \texttt{subsample\_proportion} was set to 1 in the code, but shouldn't it be
0.8? I changed it to 0.8. But it seems like you don't actually run this code,
but read existing runs, so maybe was right there?}

\textbf{Nelle: that was a mistake in the code. I don't actually run subsampling
experiments: only the bootstrap, and it's done in a separate file as it is too
time consuming to run in an Rmd file}

>>>>

@@

\CommentTok{# The function takes the data (data.frame or named matrix), the meta data}
\CommentTok{# (data.frame containing a timepoint and group column, the first corresponding}
\CommentTok{#<c2><a0>to the time-course information, the latter corresponding to the}
\CommentTok{# treatment).}
\NormalTok{DE_results =}\StringTok{ }\KeywordTok{DE_timecourse}\NormalTok{(}
\NormalTok{    data, moanin_model, timecourse_contrasts,}
    \DataTypeTok{use_voom_weights=}\OtherTok{FALSE}\NormalTok{)}
\NormalTok{pval_columns =}\StringTok{ }\KeywordTok{colnames}\NormalTok{(DE_results)[}
    \KeywordTok{grepl}\NormalTok{(}\StringTok{"pval"}\NormalTok{, }\KeywordTok{colnames}\NormalTok{(DE_results))]}
\NormalTok{qval_columns =}\StringTok{ }\KeywordTok{colnames}\NormalTok{(DE_results)[}
    \KeywordTok{grepl}\NormalTok{(}\StringTok{"qval"}\NormalTok{, }\KeywordTok{colnames}\NormalTok{(DE_results))]}
\NormalTok{pvalues =}\StringTok{ }\NormalTok{DE_results[, pval_columns]}
\NormalTok{qvalues =}\StringTok{ }\NormalTok{DE_results[, qval_columns]}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{pvalue =}\StringTok{ }\NormalTok{DE_results[, }\StringTok{"M-K_pval"}\NormalTok{]}
\KeywordTok{names}\NormalTok{(pvalue) =}\StringTok{ }\KeywordTok{row.names}\NormalTok{(DE_results)}
\NormalTok{lfc_timecourse =}\StringTok{ }\NormalTok{log_fold_change_timecourse[, }\StringTok{"M-K"}\NormalTok{]}
\KeywordTok{names}\NormalTok{(lfc_timecourse) =}\StringTok{ }\KeywordTok{row.names}\NormalTok{(log_fold_change_timecourse)}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Then rank by fisher's p-value and take max the number of genes of interest}
\CommentTok{# Filter out q-values for the pvalues table}
\NormalTok{fishers_pval =}\StringTok{ }\KeywordTok{pvalues_fisher_method}\NormalTok{(pvalues)}
\NormalTok{qvalues =}\StringTok{ }\KeywordTok{apply}\NormalTok{(pvalues, }\DecValTok{2}\NormalTok{, p.adjust)}
\NormalTok{fishers_qval =}\StringTok{ }\KeywordTok{p.adjust}\NormalTok{(fishers_pval)}

@@
